### 2016-07-18 version0.0/paper2.tex
Completed paper1 and 3
All chapter done

\chapter[SOM: classifying high $Z$ galaxies]{Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach}
\label{ch: paper2}
\defcitealias{Hossein12}{T12}
\defcitealias{Kinney96}{K96}
\defcitealias{Noll09}{N09}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction}
\label{sec: intro}
%General information about SEDs
Nearly all information we can obtain from a galaxy is encapsulated in the light it emits; every observable phenomenon in a galaxy leaves a footprint on its spectral energy distribution (SED).
We can determine some physical property of a galaxy by properly modeling various features observed in its SED, and the general shape of the SED can be used as an identifier of the morphological type.
Considering the main features of SEDs, galaxies can be categorized into two main groups: elliptical or spiral.
Each group has its own characteristic features and can in turn be divided into many sub-branches.

@@

%What \citetalias{Hossein12} did
~\citet[][hereafter \citetalias{Hossein12}]{Hossein12} classified SEDs of a sample of 142 galaxies using a supervised neural network method, based on the spectral template presented by \citetalias{Kinney96}.
With the supervised method, they could only classify SED of 105 out of the 142 galaxies.
The SED of the 37 galaxies from their samples could not be matched with any of those in the \citetalias{Kinney96} templates. 
In order to classify the remaining 37 galaxies, they combined spectrum of the \citetalias{Kinney96} templates.
%This procedure showed that, not a single type of galaxies in \citetalias{Kinney96} template could describe the SED of any of those 37 galaxies. %PB20160603: repeats previous sentence
\citetalias{Hossein12} also showed that there are tight correlations between physical properties of galaxies, and these correlations might be different for each type of galaxy.

%What we did
In this paper, we compare supervised and unsupervised methods of galaxy spectral classification directly, using exactly the same data as \citetalias{Hossein12}.  
Our hypothesis was that since a self-organizing map has the freedom to classify objects in between known classes, it could be applied to this data 
to find the best SED class for the 37 galaxies that could not be classified by the supervised method.
First, we train self-organizing maps using the \citetalias{Kinney96} spectral templates and compare our classification with the \citetalias{Kinney96} classification.
Then, we use the trained network to classify the SEDs of 142 galaxies with $0.5 < z < 1$ from \citetalias{Hossein12}. 
As in \citetalias{Hossein12}, we examine the averaged properties of the new galaxy groups and compare them with previous work.
In Section $\S$~\ref{sec: data_highZ}, we present the data that we use to train and test our networks. 
We describe the SOM methods in Section $\S$~\ref{sec: method}. 
The results of the SED classifications and a comparison with previous studies are presented in Section $\S$~\ref{sec: result}. 
In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

@@

 \subsection{Kinney spectral model}
     \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{../image_paper2/k96.jpg}
        \caption[\citet{Kinney96} spectra template for 12 types of galaxies]{\citet{Kinney96} spectra template for 12 types of galaxies from \citet{Hossein12} paper (Fig. 1 in \citet{Hossein12}). The type of each template is shown in each frame. Plots B, E, S0, Sa, Sb and SC show spectra that belong to the early types galaxies. Starburst galaxies spectra are indicated with SB 1 to 6. Higher numbers represent more intrinsic colour extinction.}
        \label{fig: k96}
    \end{figure}

@@

 \subsection{SED and properties of the sample galaxies} 
    \citetalias{Hossein12} selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field~\citep{Vanzella05, Vanzella06, Vanzella08}.
    The 142 galaxies were selected based on the availability of photometry from HST/ACS, VLA/ISAAC, and {\it Spitzer}/MIPS and IRAC (10--13 filters with $\sim 0.4<\lambda<24~\mu$m in the observed frame).
   Data from these instruments was necessary in order to have a complete picture of stellar population and star formation rate. 
    For each galaxy, a robust spectroscopic redshift and photometric measurements from the GOODS-MUSIC catalogue \citep{Santini09} was available.
   \citetalias{Hossein12} matched the point spread function (PSF) of the photometric data with \citetalias{Kinney96} data and used the photometry as inputs to the Code Investigating GALaxy Emission ({\em CIGALE});~\citep[][hereafter N09]{Noll09} to generate the best-fit SED for each galaxy.
   % as well as some of the physical properties of the galaxies.
% PB 20160603: commented out following 3 lines as I don't think this fit well here. Could maybe go somewhere else.    
%    {\em CIGALE} is a valuable tool to investigate the properties of galaxies using ultraviolet to infrared wavebands.
%    It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei optical spectral templates to model the SEDs of galaxies.
%    This code was successfully tested on data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by \citetalias{Noll09}.
    \citetalias{Hossein12} produced the best SED match, with wavelength interval of 910~\AA~to $\sim 80$~cm, for each galaxy\footnote{This wavelength interval is the default output of the {\em CIGALE} code}.
    Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr, they derived physical properties of the galaxies such as age and stellar mass.
    Some of these properties are shown in Table~\ref{tab: props}.
    In Section~\ref{sec: 1D}, we study these properties for each category.
    More details on creating SEDs and extracting information about galaxy properties using {\em CIGALE} can be found in \citetalias{Noll09} and \citetalias{Hossein12}.

@@

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Method
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{Method}
\label{sec: method}
 \subsection{Self Organizing Maps}
 \label{sec: som}

@@

 \subsubsection{Algorithm of SOM} 
 \label{sec: algorithm}
     Assume we have a dataset which contains vectors, \boldit{V} $\in \Re^n$, and we want to map them on an S1 by S2 map. 
     We start by creating S1 $\times$ S2 empty neurons. 
     The initial arrangement of these neurons depends on the map's topology provided by the user.
     In the case of 1D maps, since each neuron has two immediate neighbours, the topology of the map does not have any effect on the final result and any topology can be chosen.
     However, in 2D maps, the shape of the neurons specifies the number of immediate neighbours for each neuron and it is up to user to choose the most suitable shape based on the data.
     In this paper, we choose hexagonal topology, which gives each neuron six neighbours, and provides more interactions between neurons.
     Initially a random weight vector, \boldit{W} $\in \Re^n$, will be assigned to each node.
     The process of creating SOM happens over a series of $N$ iterations. 
     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
      In each iteration, the SOM code:
     \begin{enumerate}
        \item chooses a random vector from the dataset ($V_i$).
        \item calculates the Euclidean distance for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{min}}$"). This neuron is the winner node and is called the Best Matching Unit (BMU). 
        \item  computes the radius of the neighbourhood of the BMU to find nodes within this radius. The weight vectors of these nodes will be affected in the next steps. The radius of the neighbourhood is arbitrary and can be set to be as high as half of the SOM size. It then decays exponentially over each iteration as
        \begin{equation}
            r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
        \end{equation}
        where $\tau$ is a decay constant and is usually set to be the same as the number of iterations, $N$. $r^0_{BMU}$ and $r^t_{BMU}$ are the radii of the neighbourhood at 0th and $t$th iteration, respectively. 
        \item changes the weight vectors of the BMU and all the nodes within $r^t_{BMU}$ as:
        \begin{equation}
            \label{equ: weight adj}
            w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
        \end{equation}
        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate. $R(t)$ determines how the weight of each node in the neighbourhood of BMU will change.
     \end{enumerate}
     These steps are then repeated $N$ times.

\subsection{Creating self-organizing maps}
\label{sec: create_som}
     In order to create SOMs, we use {\sc matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.

@@

\subsection{Mock sample}

@@

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%\include{sections_highz/}{results.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Results and discussion}
\label{sec: result}

@@

    We started our analysis by creating 1D SOMs. 
    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Section~\ref{sec: 1D}).
    We generate 2D networks (Section~\ref{sec: 2D}),  again starting with the smallest possible number of neurons (4 neurons in a $2\times2$ map), increasing to 144 in a $12\times12$ map.    
    For each generated network, we compare the results with the \citetalias{Kinney96} categorization.
    We also use these networks to classify the \citetalias{Hossein12} galaxy sample, and compare this classification with that from the supervised networks in \citetalias{Hossein12}.

    \subsection{One-dimensional self-organizing maps}
    \label{sec: 1D}
        \subsubsection{Training the networks}
        \label{sec: 1Dt}
            To start our clustering, we assumed that galaxies can be divided into only two general types; quiescent and starburst.
            This corresponds to a network with only two neurons.
            We increased the size of the map gradually until the 12 input samples divide into the 12 neurons.

            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.
            As in to Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances between weight of neurons.
            As mentioned in Section~\ref{sec: method}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
            The lower panels of the figures show the number of \citetalias{Kinney96} templates that are placed in each neuron. 
            \begin{figure}
                \begin{subfigure}[b]{\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../image_paper2/1d/dist_1_by_2.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{\textwidth}
                     \includegraphics[width=\textwidth]{../image_paper2/1d/hit_t_1_by_2.png}
                \end{subfigure}
                \caption[Results of training network in $1\times2$~grid]{Results of training network in $1\times2$~grid. As in Fig.~\ref{fig: sample}, the upper panel is a distance map and the lower panel is a hit map. In this network, 5 of the templates from \citet{Kinney96} are categorized as quiescent galaxies and the rest are starbursts. Because of their strong emission lines, Sc galaxies are moved towards the starburst ones.}
                 \label{fig: 1by2T}
            \end{figure}

@@

            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
            Since there are more nodes in higher grid SOMs, the  algorithm 
            pays more attention to small differences between groups.
            If the templates from \citetalias{Kinney96} had completely distinct SEDs, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
            However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two templates and three of them are empty.
            It is evident that there was no template in the \citetalias{Kinney96} sample that can fill those empty neurons.
            In Fig.~\ref{fig: 1by12T}, from left to right, templates with types B and E, SB3 and SB4, and SB1 and SB2 are the ones grouped together. 
            The SB3 and SB4 grouping breaks when we increase the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 templates, however, remain in the same neuron until the size of the map is increased to $1\times20$~(Fig.~\ref{fig: 1by20T}).
            The separation between templates B and E only happens when the size of the SOM exceeds $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{../image_paper2/1d/dist_1_by_22.png}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{../image_paper2/1d/hit_t_1_by_22.png}
            \end{subfigure}
            \caption[Results of training network in $1\times22$~grid]{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure}

@@

        \subsubsection{Classifying the galaxy sample}
         \label{sec: 1Dv}
            After training the networks as discussed in Section~\ref{sec: 1Dt}, we used them to classify the fitted SEDs of the sample of 142 galaxies from \citetalias{Hossein12}.
            The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            Eighty of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
            The lower left panel shows the average SED of the 80 galaxies that were classified as early type 
            These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
            the SEDs clearly show the 4000\AA~break, one of the signatures of early type galaxies.
            The H$\alpha$ emission in the spectrum could be from galaxies with similar SEDs to Sa galaxies, but with stronger emission lines.
            The average SED in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
            \begin{figure}
                \begin{subfigure}[b]{\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../image_paper2/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{\textwidth}
                     \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption[Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times2$~networks]{Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times2$~network trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}). Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group. In this case 80 means that 80 of the 142 SEDs are classified into the early type group while the 62 of the 142 SEDs are categorized as starburst galaxies. Lower panel: Average SED of the galaxies in each group, early-type on the left and starburst on the right.}
                \label{fig: 1by2V}
            \end{figure}

@@

        \subsubsection{Properties of the clustered galaxies}

@@

        Fig.~\ref{fig: props} shows the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ networks.
        In all plots, the horizontal axis is the number of the neurons divided by the size of the network.%, and vertical axis is one of the aforementioned properties.
%        
        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from early type galaxies to starburst. 
       % These trends are another evidence that this method is working and can be used to categorize galaxies based on their SEDs or even their physical properties. 
        %Considering the results from Fig.~\ref{fig: props}, we can clearly see that s
        Separating galaxies based on SED types also leads to a separation in properties that derived (via {\sc CIGALE}) from the SEDs, as expected since the SED types are also based on {\sc CIGALE} fitting.

        %Sr07062016: Is it better?
        {\sc CIGALE} has various models to derive the properties of galaxies.
        Through these models, some of the properties are already known to be correlated with each other, e.g., stellar mass and star formation rate.
        \citetalias{Noll09} studied other relations between properties with no direct correlation in the models in a sample of SINGS galaxies.
        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggests that younger stellar population correlates with higher SFR.
        They also found correlations between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
        Since in the {\sc CIGALE} code, stellar mass is a free parameter, \citetalias{Noll09} argued that any stellar-mass-related correlation must be astrophysically meaningful. 
        They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
        \citetalias{Hossein12} replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than \citetalias{Noll09} results.

@@

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Summery
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Summary and future applications}
\label{sec: summary}

>>>>

\chapter[Classifying High-Redshift Galaxies Using Self-Organizing Maps]{Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach}
\label{ch: paper2}
\defcitealias{Hossein12}{T12}
\defcitealias{Kinney96}{K96}
\defcitealias{Noll09}{N09}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction}
\label{sec: intro_somz}
%General information about SEDs
Nearly all information we can obtain from a galaxy is encapsulated in the light it emits; every observable phenomenon in a galaxy leaves a footprint on its spectral energy distribution (SED).
We can determine some physical property of a galaxy by properly modeling various features observed in its SED, and the general shape of the SED can be used as an identifier of the morphological type.
Considering the main features of SEDs, galaxies can be categorized into two main groups: elliptical or spiral.
Each group has its own characteristic features and can in turn be divided into many sub-branches.

@@

%What \citetalias{Hossein12} did
~\citet[][hereafter \citetalias{Hossein12}]{Hossein12} classified SEDs of a sample of 142 galaxies using a supervised neural network method, based on the spectral template presented by \citetalias{Kinney96}.
With the supervised method, they could only classify SED of 105 out of the 142 galaxies.
The SED of the 37 galaxies from their samples could not be matched with any of those in the \citetalias{Kinney96} templates. 
In order to classify the remaining 37 galaxies, they combined spectrum of the \citetalias{Kinney96} templates.
\citetalias{Hossein12} also showed that there are tight correlations between physical properties of galaxies, and these correlations might be different for each type of galaxy.

%What we did
In this paper, we compare supervised and unsupervised methods of galaxy spectral classification directly, using exactly the same data as \citetalias{Hossein12}.  
Our hypothesis was that since a self-organizing map has the freedom to classify objects in between known classes, it could be applied to this data 
to find the best SED class for the 37 galaxies that could not be classified by the supervised method.
First, we train self-organizing maps using the \citetalias{Kinney96} spectral templates and compare our classification with the \citetalias{Kinney96} classification.
Then, we use the trained network to classify the SEDs of 142 galaxies with $0.5 < z < 1$ from \citetalias{Hossein12}. 
As in \citetalias{Hossein12}, we examine the averaged properties of the new galaxy groups and compare them with previous work.
In Section $\S$~\ref{sec: data_highZ}, we present the data that we use to train and test our networks. 
We describe the SOM methods in Section $\S$~\ref{sec: method_somz}. 
The results of the SED classifications and a comparison with previous studies are presented in Section $\S$~\ref{sec: result}. 
In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

@@

 \subsection{Kinney Spectral Model}
     \begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{../image_paper2/k96.jpg}
        \caption[\citet{Kinney96} spectra template for 12 types of galaxies]{\citet{Kinney96} spectra template for 12 types of galaxies from \citet{Hossein12} paper (Fig. 1 in \citet{Hossein12}). The type of each template is shown in each frame. Plots B, E, S0, Sa, Sb and SC show spectra that belong to the early types galaxies. Starburst galaxies spectra are indicated with SB 1 to 6. Higher numbers represent more intrinsic colour extinction.}
        \label{fig: k96}
    \end{figure}

@@

 \subsection{SED and Properties of the Sample Galaxies} 
    \citetalias{Hossein12} selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field~\citep{Vanzella05, Vanzella06, Vanzella08}.
    The 142 galaxies were selected based on the availability of photometry from HST/ACS, VLA/ISAAC, and {\it Spitzer}/MIPS and IRAC (10--13 filters with $\sim 0.4<\lambda<24~\mu$m in the observed frame).
   Data from these instruments was necessary in order to have a complete picture of stellar population and star formation rate. 
    For each galaxy, a robust spectroscopic redshift and photometric measurements from the GOODS-MUSIC catalogue \citep{Santini09} was available.
   \citetalias{Hossein12} matched the point spread function (PSF) of the photometric data with \citetalias{Kinney96} data and used the photometry as inputs to the Code Investigating GALaxy Emission ({\em CIGALE});~\citep[][hereafter N09]{Noll09} to generate the best-fit SED for each galaxy.
    \citetalias{Hossein12} produced the best SED match, with wavelength interval of 910~\AA~to $\sim 80$~cm, for each galaxy\footnote{This wavelength interval is the default output of the {\em CIGALE} code}.
    Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr, they derived physical properties of the galaxies such as age and stellar mass.
    Some of these properties are shown in Table~\ref{tab: props}.
    In Section~\ref{sec: 1D_somz}, we study these properties for each category.
    More details on creating SEDs and extracting information about galaxy properties using {\em CIGALE} can be found in \citetalias{Noll09} and \citetalias{Hossein12}.

@@

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Method
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Method}
\label{sec: method_somz}
 \subsection{Self Organizing Maps}
 \label{sec: som}

@@

\subsubsection{Algorithm of SOM} 
   \label{sec: algorithm_somz}

     Assume we have a dataset which contains vectors, \boldit{V} $\in \Re^n$, and we want to map them on an S1 by S2 map. 
     We start by creating S1 $\times$ S2 empty neurons. 
     The initial arrangement of these neurons depends on the map's topology provided by the user.
     In the case of 1D maps, since each neuron has two immediate neighbours, the topology of the map does not have any effect on the final result and any topology can be chosen.
     However, in 2D maps, the shape of the neurons specifies the number of immediate neighbours for each neuron and it is up to user to choose the most suitable shape based on the data.
     In this paper, we choose hexagonal topology, which gives each neuron six neighbours, and provides more interactions between neurons.
     Initially a random weight vector, \boldit{W} $\in \Re^n$, will be assigned to each node.
     The process of creating SOM happens over a series of $N$ iterations. 
     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
      In each iteration, the SOM code:
     \begin{enumerate}
        \item chooses a random vector from the dataset ($V_i$).
        \item calculates the Euclidean distance for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{min}}$"). This neuron is the winner node and is called the Best Matching Unit (BMU). 
        \item  computes the radius of the neighbourhood of the BMU to find nodes within this radius. The weight vectors of these nodes will be affected in the next steps. The radius of the neighbourhood is arbitrary and can be set to be as high as half of the SOM size. It then decays exponentially over each iteration as
        \begin{equation}
            r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
        \end{equation}
        where $\tau$ is a decay constant and is usually set to be the same as the number of iterations, $N$. $r^0_{BMU}$ and $r^t_{BMU}$ are the radii of the neighbourhood at 0th and $t$th iteration, respectively. 
        \item changes the weight vectors of the BMU and all the nodes within $r^t_{BMU}$ as:
        \begin{equation}
            \label{equ: weight adj}
            w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
        \end{equation}
        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate. $R(t)$ determines how the weight of each node in the neighbourhood of BMU will change.
     \end{enumerate}
     These steps are then repeated $N$ times.

\subsection{Creating Self-Organizing Maps}
\label{sec: create_som}
     In order to create SOMs, we use {\sc matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.

@@

\subsection{Mock Sample}

@@

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%\include{sections_highz/}{results.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Results and Discussion}
\label{sec: result}

@@

    We started our analysis by creating 1D SOMs. 
    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Section~\ref{sec: 1D_somz}).
    We generate 2D networks (Section~\ref{sec: 2D}),  again starting with the smallest possible number of neurons (4 neurons in a $2\times2$ map), increasing to 144 in a $12\times12$ map.    
    For each generated network, we compare the results with the \citetalias{Kinney96} categorization.
    We also use these networks to classify the \citetalias{Hossein12} galaxy sample, and compare this classification with that from the supervised networks in \citetalias{Hossein12}.

    \subsection{One-Dimensional Self-Organizing Maps}
    \label{sec: 1D_somz}
        \subsubsection{Training the Networks}
        \label{sec: 1Dt}
            To start our clustering, we assumed that galaxies can be divided into only two general types; quiescent and starburst.
            This corresponds to a network with only two neurons.
            We increased the size of the map gradually until the 12 input samples divide into the 12 neurons.

            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.
            As in to Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances between weight of neurons.
            As mentioned in Section~\ref{sec: method_somz}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
            The lower panels of the figures show the number of \citetalias{Kinney96} templates that are placed in each neuron. 
            \begin{figure}
                \begin{subfigure}[b]{\textwidth}
                    \centering
                    \includegraphics[width=0.8\textwidth]{../image_paper2/1d/dist_1_by_2.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{\textwidth}
                     \includegraphics[width=0.8\textwidth]{../image_paper2/1d/hit_t_1_by_2.png}
                \end{subfigure}
                \caption[Results of training network in $1\times2$~grid]{Results of training network in $1\times2$~grid. As in Fig.~\ref{fig: sample}, the upper panel is a distance map and the lower panel is a hit map. In this network, 5 of the templates from \citet{Kinney96} are categorized as quiescent galaxies and the rest are starbursts. Because of their strong emission lines, Sc galaxies are moved towards the starburst ones.}
                 \label{fig: 1by2T}
            \end{figure}

@@

            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} in Appendix~\ref{app: high_Z_1d_soms} and ~\ref{fig: 1by22T}).
            Since there are more nodes in higher grid SOMs, the  algorithm 
            pays more attention to small differences between groups.
            If the templates from \citetalias{Kinney96} had completely distinct SEDs, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
            However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two templates and three of them are empty.
            It is evident that there was no template in the \citetalias{Kinney96} sample that can fill those empty neurons.
            In Fig.~\ref{fig: 1by12T}, from left to right, templates with types B and E, SB3 and SB4, and SB1 and SB2 are the ones grouped together. 
            The SB3 and SB4 grouping breaks when we increase the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 templates, however, remain in the same neuron until the size of the map is increased to $1\times20$~(Fig.~\ref{fig: 1by20T}).
            The separation between templates B and E only happens when the size of the SOM exceeds $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{../image_paper2/1d/dist_1_by_22.png}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{../image_paper2/1d/hit_t_1_by_22.png}
            \end{subfigure}
            \caption[Results of training network in $1\times22$~grid]{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure}

@@

        \subsubsection{Classifying the Galaxy Sample}
         \label{sec: 1Dv}
            After training the networks as discussed in Section~\ref{sec: 1Dt}, we used them to classify the fitted SEDs of the sample of 142 galaxies from \citetalias{Hossein12}.
            The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            Eighty of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
            The lower left panel shows the average SED of the 80 galaxies that were classified as early type 
            These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
            the SEDs clearly show the 4000\AA~break, one of the signatures of early type galaxies.
            The H$\alpha$ emission in the spectrum could be from galaxies with similar SEDs to Sa galaxies, but with stronger emission lines.
            The average SED in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
            \begin{figure}
                \begin{subfigure}[b]{\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../image_paper2/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{\textwidth}
                     \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption[Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times2$~networks]{Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times2$~network trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}). Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group. In this case 80 means that 80 of the 142 SEDs are classified into the early type group while the 62 of the 142 SEDs are categorized as starburst galaxies. Lower panel: Average SED of the galaxies in each group, early-type on the left and starburst on the right.}
                \label{fig: 1by2V}
            \end{figure}

@@

        \subsubsection{Properties of the Clustered Galaxies}

@@

        Fig.~\ref{fig: props} shows the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ networks.
        In all plots, the horizontal axis is the number of the neurons divided by the size of the network.%, and vertical axis is one of the aforementioned properties.
%        
        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from early type galaxies to starburst. 
       Separating galaxies based on SED types also leads to a separation in properties that derived (via {\em CIGALE}) from the SEDs, as expected since the SED types are also based on {\em CIGALE} fitting.

        {\em CIGALE} has various models to derive the properties of galaxies.
        Through these models, some of the properties are already known to be correlated with each other, e.g., stellar mass and star formation rate.
        \citetalias{Noll09} studied other relations between properties with no direct correlation in the models in a sample of SINGS galaxies.
        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggests that younger stellar population correlates with higher SFR.
        They also found correlations between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
        Since in the {\em CIGALE} code, stellar mass is a free parameter, \citetalias{Noll09} argued that any stellar-mass-related correlation must be astrophysically meaningful. 
        They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
        \citetalias{Hossein12} replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than \citetalias{Noll09} results.

@@

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Summery
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Summary and Future Applications}
\label{sec: summary}
